---
title: "API"
author: ""
date: '2022-09-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Working with Petitions API

- The petition information is also available through API
- To access, you construct a URL for JSON, then
  1. Get JSON
  2. Parse JSON
  3. Convert it to a DataFrame




```{r}
library(tidyverse)
library(jsonlite)

```

# Inflation petitions

- To limit a size of JSON, let's check "inflation" related petitions


```{r}
url <- 'https://petition.parliament.uk/petitions.json?page=1&q=inflation&state=open'

```


# Let's try `read_json()` 

```{r}
js <- read_json(url)
```



## Get some variables and generate a DF

- fields: action, additional_details, background
- use `purrr::pluck()`


```{r}

```

## `unnest`

- The previous example is too complicated
- `unnest()` will help you a lot

```{r}

```

- This method works with similarly structured XML


```{r eval=F}
library(xml2)
xml <- read_xml(url) %>% 
  as_list()
# Then do unnesting
```



# Let's try fromJSON

- use `jsonlite::fromJSON()`, see what happens
- this is actually so easy

```{r}

```


# More detailed info for each petition

- Using the petition ids from the previous example, get the number of signatures in each electoral constituency
- API access point is: `https://petition.parliament.uk/petitions/***.json` where `***` is petition id.

```{r}
url_template <- 'https://petition.parliament.uk/petitions/%s.json'
url <- sprintf(url_template, '614869')
```


```{r}

```
